A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-10-02 manuscript.Rmd
swap order of Michèle and anonymous reviewer
containing the project -> project directory closes #72

authornote: |
   We are grateful to Julia Delius for her helpful assistance in language and style editing. We thank the anonymous reviewer and Michèle Nuijten, and all contributors of our GitHub repository for helpful feedback on the paper. This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompanying GitHub repository: [https://github.com/aaronpeikert/reproducible-research/](https://github.com/aaronpeikert/reproducible-research/). This document is based on the commit identified by hash `"`r system2("git", "rev-parse --short HEAD", stdout = TRUE)`"`. To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the GitHub repository of our paper at [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).

@@

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/reproducible-research.git
# (2) enter the directory containing the project
cd reproducible-research
# (3) run the analysis/data preparation etc. with the local R installation
make all
```

@@

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/reproducible-research.git
# (2) enter the directory containing the project
cd reproducible-research
# (3) build the docker container
make build
# (4) run the analysis and produce the final PDF inside the container
make all DOCKER=TRUE
```

>>>>

authornote: |
   We are grateful to Julia Delius for her helpful assistance in language and style editing. We thank Michèle Nuijten and the anonymous reviewer, and all contributors of our GitHub repository for helpful feedback on the paper. This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompanying GitHub repository: [https://github.com/aaronpeikert/reproducible-research/](https://github.com/aaronpeikert/reproducible-research/). This document is based on the commit identified by hash `"`r system2("git", "rev-parse --short HEAD", stdout = TRUE)`"`. To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the GitHub repository of our paper at [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).

@@

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/reproducible-research.git
# (2) enter the project directory
cd reproducible-research
# (3) run the analysis/data preparation etc. with the local R installation
make all
```

@@

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/reproducible-research.git
# (2) enter the project directory
cd reproducible-research
# (3) build the docker container
make build
# (4) run the analysis and produce the final PDF inside the container
make all DOCKER=TRUE
```
